Bounds on the dimension of consistent convex surrogates

### 2020-05-25 neurips-20/cvx-flats.tex
Added lemmas for dimension generalization.

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\simplex}{\Delta_\Y}
\newcommand{\relint}[1]{\mathrm{relint}(#1)}
\newcommand{\prop}[1]{\mathrm{prop}[#1]}
\newcommand{\elic}{\mathrm{elic}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
\newcommand{\ccdim}{\mathrm{ccdim}}
\newcommand{\codim}{\mathrm{codim}}
\newcommand{\propdis}{\mu}

@@

\title{cvx-flats}

@@

\begin{corollary}[\cite{ramaswamy2016convex}]
	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
	Take $p \in \simplex$ and $r \in \R$ such that $p \in \gamma_r$.
	\begin{equation}
	\ccdim(\ell) \geq \|p\|_0 - \dim(\S_{\gamma_r}(p)) - 1~.~
	\end{equation}
\end{corollary}

>>>>

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\simplex}{\Delta_\Y}
\newcommand{\relint}[1]{\mathrm{relint}(#1)}
\newcommand{\prop}[1]{\mathrm{prop}[#1]}
\newcommand{\elic}{\mathrm{elic}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
\newcommand{\ccdim}{\mathrm{ccdim}}
\newcommand{\codim}{\mathrm{codim}}
\newcommand{\supp}{\mathrm{supp}}
\newcommand{\spn}{\mathrm{span}}
\newcommand{\propdis}{\mu}

@@

\title{Bounds on the dimension of consistent convex surrogates}

@@

\begin{lemma}\label{lem:p-boundary-fstar}
	For a given property $\gamma$, fix $p \in \simplex$ and $r \in\R$ so that $r \in \gamma(p)$.
	Consider the flat $F'$ containing $p$ of dimension at least $n-d-1$.
	The flat $F^* = F' \cap \spn(\{e_y : y \in \supp(p)\})$ has dimension $\dim(F') - (n - \|p\|_0)$.
\end{lemma}
\begin{proof}
	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
	\begin{align*}
	\dim(F^*) &= \dim(F') + \|p\|_0 - \dim(F' + P)
	\end{align*}
	The claim then holds if $n = \dim(F' + P)$.
	\jessie{This is where I'm stuck??}
\end{proof}

\begin{lemma}\label{lem:p-boundary-fsd}
	For any $p \in \simplex$ and $r$ such that $p \in \gamma_r$, we have $\dim(\S_{\gamma_r}(p)) = \dim(\S'_{\gamma_r}(p))$, where $\S_{\gamma_r}(p) := \S_{\gamma_r}(p) \cap \spn(\{e_y : y \in \supp(p) \}$.
\end{lemma}
\begin{proof}
	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
	\begin{align*}
	\dim(\S'_{\gamma_r}(p)) &= \dim(\S_{\gamma_r}(p)) + \dim(P) - \dim(\S_{\gamma_r}(p) + P)
	\end{align*}
	If $\dim(P) = \dim(\S_{\gamma_r}(p) + P)$, the claim holds.
	Be definition of $P$, we know $\dim(P) = \|p\|_0$, so we can show $\dim(\S_{\gamma_r}(p) + P) = \|p\|_0$.		\jessie{This is where I'm stuck??}

\begin{corollary}[\cite{ramaswamy2016convex}]
	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
	Take $p \in \simplex$ and $r \in \R$ such that $p \in \gamma_r$.
	\begin{equation}
	\ccdim(\ell) \geq \|p\|_0 - \dim(\S_{\gamma_r}(p)) - 1~.~
	\end{equation}
\end{corollary}
\begin{proof}
	Let $L : \reals^d \times \Y \to \reals$ be a calibrated surrogate for $\ell$.
	First, for intuition, consider $p \in \relint{\simplex}$. 
	Theorem~\ref{thm:cvx-flats} implies that there exists a flat $F'$ of affine dimension at least $n-d-1$.
	Lemma~\ref{lem:feas-sub-is-a-flat} then says that $\dim(\S_{\gamma_r}(p)) \geq \dim(F') \geq n-d-1 \implies d \geq n - \dim(\S_{\gamma_r}(p)) - 1$.

	Now, if $p \not \in \relint{\simplex}$, we can apply Lemma~\ref{lem:p-boundary-fstar} to observe the existence of an $F^*$ with dimension $\dim(F') - (n - \|p\|_0)$.
	Moreover, since projecting to $(\{e_y : y \in \supp(p)\})$ does not change the feasible subspace dimension, so we observe the result.
\end{proof}
